Read Me

### 2023-04-30 code/analysis_code/1_EDA_alt.Rmd
hopefully this corrects things...

```{r}
pos_predictors <- race_sub %>% 
  select(c("Median Household Income",
           "Percent Living in Poverty",
           "Percent Without an Internet subscription",
           "Percent Uninsured Under 65 Years Old",
           "Percent Living with Food Insecurity",
           "Percentage Diagnosed Late")) %>% 
  names()
```

>>>>

```{r}
pos_predictors <- race_sub %>%
  ungroup() %>% 
  select(c("Median Household Income",
           "Percent Living in Poverty",
           "Percent Without an Internet subscription",
           "Percent Uninsured Under 65 Years Old",
           "Percent Living with Food Insecurity",
           "Percentage Diagnosed Late")) %>% 
  names()
```

### 2023-04-30 code/analysis_code/2_pca_alt.Rmd
hopefully this corrects things...

race_sub <- readRDS(here("data/processed_data/race_alt.rds"))
pos_predictors <- readRDS(here("data/processed_data/pos_predictors.rds"))
sub <-race_sub %>% 
  select(contains(c("State", "Race", "Ratio")), matches(pos_predictors))
```

PCA
```{r}
#Setting up correlation matrix
pca_1 <- race_sub %>% 
  select(all_of(pos_predictors)) %>% 
  select(-contains("Late")) %>%  ##poorly correlated
  cor() %>% 
  ggcorrplot()

>>>>

race_sub <- readRDS(here("data/processed_data/race_alt.rds"))
race_sub <- race_sub %>% ungroup()
pos_predictors <- readRDS(here("data/processed_data/pos_predictors.rds"))
sub <-race_sub %>% 
  select(contains(c("State", "Race", "Ratio")), matches(pos_predictors))
```

PCA
```{r}
#Setting up correlation matrix
pca_1 <- race_sub %>% 
  ungroup() %>% 
  select(all_of(pos_predictors)) %>% 
  select(-contains("Late")) %>%  ##poorly correlated
  cor() %>% 
  ggcorrplot()

### 2023-04-30 code/analysis_code/p4_mapping.Rmd
hopefully this corrects things...

df_fit <- readRDS(here("data/processed_data/df_fit_alt.rds"))
df_raw <- readRDS(here("data/processed_data/race_alt.rds"))
```

@@

Next, I will merge my dataframe contain the variables of interest with the spatial object. 
```{r}
df_sf_fit<- merge(states,df_fit, by = "region")
# This next step is import to ensure that no "holes" appear in the map.
df_sf_fit <- df_sf_fit[order(df_sf_fit$order), ]
```

>>>>

df_fit <- readRDS(here("data/processed_data/df_fit_alt.rds"))
```

@@

Next, I will merge my dataframe contain the variables of interest with the spatial object. 
```{r}
df_sf_fit <- merge(states,df_fit, by = "region")
# This next step is import to ensure that no "holes" appear in the map.
df_sf_fit <- df_sf_fit[order(df_sf_fit$order), ]
```
